Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-05-02 analysis/paper/paper.Rmd
Replace "Table" with "Tab."

# table captions
tn <- local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('\n\nTable ', i, ': ', x, sep = '')
    # The : before Table tells pandoc to wrap your caption in <caption></caption>
  }
})
knitr::knit_hooks$set(tab.cap = function(before, options, envir) {
  if (!before)
    tn(options$tab.cap)
})
default_output_hook = knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == F)  
    x
  else
    default_output_hook(x,options)
})

@@

The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Table \@ref(tab:N-rates)).

@@

Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Table \@ref(tab:N-rates)).

>>>>

# table captions
tn <- local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('\n\nTab. ', i, ': ', x, sep = '')
    # The : before Table tells pandoc to wrap your caption in <caption></caption>
  }
})
knitr::knit_hooks$set(tab.cap = function(before, options, envir) {
  if (!before)
    tn(options$tab.cap)
})
default_output_hook = knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == F)  
    x
  else
    default_output_hook(x,options)
})

@@

The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Tab. \@ref(tab:N-rates)).

@@

Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Tab. \@ref(tab:N-rates)).
